---
title: "TrainingTemplate"
author: "Unity Tambellini-Smith"
date: "2024-03-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#import tidyverse library
```{r}

```

#import data 
```{r, echo=FALSE}

```

#find column names
```{r}

```

#Looking at the data -- view, head, summary
```{r}

```

#looking at a table of 'school' values
```{r}

```

#filter for the institution assigned to you
```{r}

```

#change year to be a factor
```{r}

```

#create a new column to find room and board 
```{r}
```

#pivot long to prepare for graphing where value is the amount in $ and the group column is either tuition or room and board. change new column to be a factor
```{r}

```

##basic plot
resources on stacked bar charts:
https://r-graph-gallery.com/48-grouped-barplot-with-ggplot2

#plot a stacked bar chart where the x axis is year the y axis is amount, and it is grouped by tuition vs room and board
```{r}

```
it might be better to have the room and board value on the bottom: so we do the following 

#add title, change y axis to be "amount in dollars", and change font to Palatino
```{r}


```

#make a black and white version 
```{r}

```

#export 
```{r}

```
